Fine-scale Data Reveals Neighborhood Inequalities Effects of Heat on Expressed Mood

### 2021-06-23 doc/temp-sentiment.tex
Updates from Overleaf

\subsection*{Overall Effect}
We examine the relationship between the sentiment expressed in Tweets and the prevailing Wet Bulb Globe Temperature (WBGT), a temperature metric that accounts for dry-bulb temperature, humidity, wind speed, and solar radiation to more accurately describe the effects of heat on the human body \cite{budd2008wet}. Controlling for a variety of fixed effects across all Tweets, we find higher temperatures are associated with lower sentiment (i.e., worsening mood; See Fig. \ref{fig:wbgt}).  Sentiment is highest at 5\textdegree C WBGT (a dry bulb temperature typically around 12\textdegree C/54\textdegree F) with the largest declines in sentiment between 20\textdegree -25\textdegree C WBGT (dry bulb 29\textdegree-36\textdegree C/84\textdegree-97\textdegree F). Sentiment also declines with colder temperatures (below 5\textdegree C WBGT), although only slightly. We ran models using multiple measures of sentiment and find similar results and patterns across all sentiment measures (see Supplement).

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\linewidth]{../res/wbgt.png}
  \caption{Relationship between Wet Bulb Globe Temperature (WBGT) and sentiment from text in Tweets.  As temperatures increase above 5\textdegree C WBGT, sentiment rapidly declines.}
  \label{fig:wbgt}
\end{figure}

We find median neighborhood income strongly moderates the relationship between temperature and sentiment (see Fig \ref{fig:hetero}, panel A), with large differences in sentiment between the poorest and wealthiest neighborhoods. As temperatures increase to a modest 20\textdegree C WBGT (29\textdegree C/84\textdegree F), sentiment increases in the wealthiest neighborhoods (95th income percentile) but decreases in the median and lowest income neighborhoods. The wealthiest neighborhoods do not see decreases in sentiment until temperatures exceed 20\textdegree C WBGT (29\textdegree C/84\textdegree F), at which point sentiment decreases relatively evenly regardless of neighborhood income percentile.

>>>>

\subsection*{Overall Effect}
We examine the relationship between the mood expressed in Tweets and the prevailing Wet Bulb Globe Temperature (WBGT), a temperature metric that accounts for dry-bulb temperature, humidity, wind speed, and solar radiation to more accurately describe the effects of heat on the human body \cite{budd2008wet}. Controlling for a variety of fixed effects across all Tweets, we find higher temperatures are associated with worsened mood (Fig. \ref{fig:wbgt}).  Mood is highest at 5\textdegree C WBGT (a dry bulb temperature typically around 12\textdegree C/54\textdegree F) with the largest declines between 20\textdegree -25\textdegree C WBGT (dry bulb 29\textdegree-36\textdegree C/84\textdegree-97\textdegree F). Mood also declines with colder temperatures (below 5\textdegree C WBGT), although only slightly. We estimated mood using the Valence Aware Dictionary for Sentiment Reasoning (VADER) method in our main analysis \cite{gilbert_vader_2014}, although using other methods yield similar results (see Supplement).

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\linewidth]{../res/wbgt.png}
  \caption{Relationship between Wet Bulb Globe Temperature (WBGT) and expressed mood in Tweets.  As temperatures increase above 5\textdegree C WBGT, mood rapidly declines.}
  \label{fig:wbgt}
\end{figure}

We find that mean neighborhood income strongly moderates the relationship between temperature and sentiment (Fig. \ref{fig:hetero}, panel A), with large differences in sentiment between the poorest and wealthiest neighborhoods. As temperatures increase to a modest 20\textdegree C WBGT (29\textdegree C/84\textdegree F), sentiment increases in the wealthiest neighborhoods (95th income percentile) but decreases in the median and lowest income neighborhoods. The wealthiest neighborhoods do not see decreases in sentiment until temperatures exceed 20\textdegree C WBGT (29\textdegree C/84\textdegree F), at which point sentiment decreases relatively evenly regardless of neighborhood income percentile.
